Optimal updating factor in Wang-Landau and metadynamics simulations

### 2016-01-09 doc/invt.tex
invt.c: multiple-bin update

\begin{abstract}
  Wang-Landau (WL) and metadynamics algorithms
  are widely-used techniques in free energy simulations.
  %
  These techniques allow one to sample a flat distribution
  along a quantity of interest
  by adaptively constructing a bias potential,
  as the negative potential of mean force (PMF).
  %
  However, the asymptotic error of the resulting PMF
  is determined by the magnitude of updating the bias potential,
  and in what fashion the magnitude is reduced
  over the simulation time.
  %
  In the Wang-Landau case,
  a simple and effective formula for the magnitude
  is given by the inverse of the number of simulation steps.
  %
  Here, we shall reexamine the optimality of this prescription,
  and attempt to extend it to the metadynamics case,
  in which the bias potential at several neighboring bins
  are updated according to a predetermined window function,
  upon each visit.
  %
  Our analysis also suggests that in terms of the convergence
  the WL algorithm represents one of the best of the class
  updating schemes among more sophisticated candidates.
\end{abstract}

>>>>

\begin{abstract}
  Wang-Landau (WL) and metadynamics algorithms
  are widely-used techniques in free energy simulations.
  %
  These techniques allow one to sample a flat distribution
  along a quantity of interest
  by adaptively constructing a bias potential,
  as the negative potential of mean force (PMF).
  %
  However, the asymptotic error of the resulting PMF
  is determined by the magnitude of updating the bias potential,
  and in what fashion the magnitude is reduced
  over the simulation time.
  %
  In the Wang-Landau case,
  a simple and effective formula for the magnitude
  is given by the inverse of the number of simulation steps.
  %
  Here, we shall reexamine the optimality of this prescription,
  and attempt to extend it to the metadynamics case,
  in which the bias potential at several neighboring bins
  are updated according to a predetermined window function,
  upon each visit.
  %
  Our analysis also suggests that in terms of convergence
  the WL algorithm represents one of the best of the class
  updating schemes among more sophisticated candidates.
\end{abstract}
